Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-22 doc/paper.Rmd
crossvalidation files

```{r}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
errorsCV <- 
  rbind(errorrate(cvcs2, 0.001), 
        errorrate(cvcs2, 0.005), 
        errorrate(cvcs2, 0.01), 
        errorrate(cvcs2, 0.05))

errorsCV %>% 
  ggplot(aes(x = wo, y = beta)) + 
  geom_point(aes(colour = factor(alpha))) +
  geom_line(aes(colour = factor(alpha))) +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  theme_bw()

>>>>

\autoref{fig:type2} gives an overview of the type 2 error rates of methods CS1 and CS2 over a range of different optimization window sizes $w_o$.

```{r type2, fig.height = 5, fig.width = 5, out.width='0.7\\textwidth', fig.cap="Side-by-side comparison of type II error rates of methods CS1 and CS2 by size of optimization window $w_o$."}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
errorsCV <- 
  rbind(errorrate(cvcs2, 0.001), 
        errorrate(cvcs2, 0.005), 
        errorrate(cvcs2, 0.01), 
        errorrate(cvcs2, 0.05))
errorsCV$method <- "CS2"

errorsCV %>% 
  ggplot(aes(x = wo, y = beta)) + 
  geom_point(aes(colour = factor(alpha))) +
  geom_line(aes(colour = factor(alpha))) +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  theme_bw() +
  facet_grid(.~method, labeller="label_both")
